\documentclass[12pt]{article}
\usepackage{multicol}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage[top=1cm, bottom=2cm, left=2cm, right=2cm]{geometry}
%\setlength{\topmargin}{0in}
%\setlength{\headheight}{0in}
%\setlength{\headsep}{0in}

\begin{document}
%\thispagestyle{empty}
 %\input{./title.tex}
\begin{center}

\textsc{\huge \textit{Curriculum Vitae}}
\\[0.5cm]
\textsc{\Large Anoop Kumar Malav}
 \\[0.1cm]

\textit{\large Python/Django Developer} \\
\addvspace{0.04cm}
\rule[0.07cm]{17.52cm}{0.01cm}
\begin{tabular}{l c l}
Organization      &:& Finoit Technologies Pvt. Ltd. Noida \\
Department        &:& Web Development \\
Email ID          &:& anoop.k.malav@gmail.com \\
Contact No.       &:& +91-9971919916 \\
\end{tabular}

\addvspace{0.02cm}
\rule[0.02cm]{17.52cm}{0.01cm}
\end{center}

\section*{Objective}
Accelerate my pace towards the growth of the organization by riding on my strength and
to make innovations with my talented skills.

\section*{Summary of Qualifications}

\begin{itemize}
 \item Significant experience with Django and Django REST Framework.
 \item Developed Reusable Components for Django and Django REST Framework.
 \item Awarded Certificate Of Excellence from Finoit Technologies for year 2014.
 \item First Finoit Member to start using GIT for Source Code Management.
 \item Provided Training to Team Members of Linux, GIT, Python, Django, REST.
 \item Always appreciated by Team Manager for Project Quality, Documention and Fast Delivery.
     \begin{comment}
 \item Always follow best practices, write well formatted and documented code.
 \item Prefer to deliver documentation along with product. Work hard to meet the deadlines.
 \item Prefer playing with the code in shell, before writing it in the module.
 \item Mostly prefer quality over quantity. Good quality reduces maintenance cost, and increases productivity. In case of urgency of task completion, may compromise with quality for short period of time, but later its taken care of.
 \item Prefer to work based on DRY principle, i.e. writing mixins and utils and plugging these directly instead of writing repetitive code.
 \item Enjoy working on Linux Server, GIT as Source Code Management Tool and Vim as Text-Editor.
     \end{comment}
\end{itemize}


\section*{Technical Skills}

\subsubsection*{Hand On Experience}

\begin{tabular}{l l l l l l}
 $\circ$ Python &
 $\circ$ Django &
 $\circ$ Django Rest Framework &
 $\circ$ GIT &
 $\circ$ Vim &
 $\circ$ Ubuntu \\
\end{tabular}

\subsubsection*{Knowledge Of}

\begin{tabular}{l l l l}
 $\circ$ C &
 $\circ$ JavaScript &
 $\circ$ \LaTeX{} &
 $\circ$ Google Cloud Engine \\
 $\circ$ Java &
 $\circ$ JQuery &
 $\circ$ Amazon Web Services &
 $\circ$ OAuth2 \\
 $\circ$ Nginx &
 $\circ$ Apache &
 $\circ$ Gunicorn &
 $\circ$ Supervisor: A Process Control System \\
 $\circ$ Ajax &
 $\circ$ HTML &
 $\circ$ Continuous Integration &
 $\circ$ Github / GitLab / Gitolite \\
 % Markdown
\end{tabular}

\subsubsection*{Little Experience With}

\begin{tabular}{l l l l l l}
 $\circ$ MySQL &
 $\circ$ PostgreSQL &
 $\circ$ Shell Script &
 $\circ$ XMPP &
 $\circ$ JSP &
% $\circ$ Prolog \\
% $\circ$ Socket &
 $\circ$ WAMP Server \\
% $\circ$ LDAP \\
% $\circ$ SCRUM Development \\
\end{tabular}

\begin{comment}
\section*{Interested In}

\begin{itemize}
 \item Security
 \item Automated testing \& Test-Driven Development
 \item Core Python and Linux Tasks
 \item Server Management (Deployment of large scale web application)
 \item Technologies such as Redis \& MongoDB
 \item RESTful Web Services
\end{itemize}

\section*{Area of Interest}
%\begin{center}

\begin{tabular}{l l l}

$\bullet$  Computer Programming &
$\bullet$  Data Structures and Algorithms &
$\bullet$  Operating Systems \\
$\bullet$  Computer Networks &
$\bullet$  Computer Vision and Pattern Recognition & \\
\end{tabular}
%\end{center}

\section*{Technical Proficiency}
\begin{tabular}{l c l}
Programming & : & C, Java, Prolog \\
Web Development & : & HTML, CSS, PHP, JavaScript, MySQL, GIMP \\
Operating System & : & GNU/Linux, Windows \\
Others & : & \LaTeX{} , OpenCV(Image Processing), System Programming under Linux, Unix Shell \\
\end{tabular}

\section*{Projects}
\begin{itemize}
 \item \textbf{Colored CCA (Connected Component Analysis)}
 \\ \textit{Technology Used : OpenCV (Image Processing)}
 \item \textbf{Minesweeper}
 \\ Java based mines game applet.
 \item \textbf{LAN Radio Server}
\\ Real-Time Sound streaming with different channels on LAN.
\\ \textit{Technology used : Socket Programming in JAVA}
 \item \textbf{Digital Music Server}
\\ A common DMS for all users on LAN.
\\ \textit{Technology used : Socket Programming in JAVA, MyID3: a Java ID3 Tag Library.}
 \item \textbf{PDF Digger}
\\ Scans the given set of research papers(PDF) and predicts the person’s research interest.
\\ \textit{Technologies Used: Java, IText Library}
 \item \textbf{MP3 Manager}
\\ Scans the given collection of songs and predicts the genre in which user
mostly interested in and also manage the collection of songs by  re-arranging them
in hierarchy of $Year \rightarrow Album \rightarrow Song.$
\\ \textit{Technologies Used: Java, ID3 Library}
 \item \textbf{Route Planner / Airline Scheduler}
 \\Finds all possible flights from specified source
to specified destination on a specified date.
\\ \textit{Technology Used : Prolog}

\end{itemize}
\end{comment}

\section*{Work Experience [Finoit, Aug 2012 to Present]}
\begin{itemize}
 \item \textbf{Veris (Visitor Management System)}
    \\ Facilitates the users to setup meetings and relay information to the Visitor Management System for Check-ins, all in a completely secured and hassle free environment.
    \\ \textit{Technology used : Python3.4, Django1.8, Django-Rest-Framework, PostgreSQL, Django-MPTT, Django-storages, libphonenumbers.}
 \item \textbf{Triplinks (Social Network for lone business travellers)}
    \\ TripLinks connects lone travellers with other travellers and locals. Share dinner, a coffee or a run after a work.
    \\ \textit{Technology used : Python3.4, Django1.8, Django-Rest-Framework, PostgreSQL, Datatables.}
 \item \textbf{SplitKart (Payment Split System)}
    \\ Get restaurant deals, plan outing and split bills among friends, family and colleagues.
    \\ \textit{Technology used : Python3.4, Django1.7, Django-Rest-Framework, PostgreSQL, Datatables.}
 \item \textbf{NOC (Network Operations Center)}
    \\ Manage Network Devices, GIS Inventory and Device Services Status.
    \\ Track performance of devices. Raise alarms for bad status of device services.
    \\ \textit{Technology Used : Python2.7, Django-1.6, MySQL, South, Django-MPTT, Celery, jQuery, Highcharts, Datatables.}
 \item \textbf{UPVGO (e-learning platform)}
    \\ Students can play apps and complete assignments.
    \\ Teachers and parents can assign assignments, track performance of students.
    \\ \textit{Technology used : Python2.7, Django1.6, Django-Rest-Framework, MySQL, OAuth2.}
 \item \textbf{EMEND (e-learning app for CAT preparations)}
    \\ Manage CAT Practice Questions. Integration with UPVGO. APIs for GamePlay and Reports.
    \\ \textit{Technology used : Python3.4, Django1.7, Django-Rest-Framework, PostgreSQL.}
 \item \textbf{Budgle (Expense Tracker)}
    \\ Track expenses and share with friends.
    \\ \textit{Technology used : Python3.4, Django1.7, Django-Rest-Framework, PostgreSQL, OAuth2.}
 \item \textbf{Workflow (Office Management System)}
    \\ Manage employees, Leaves, Attendance and Time-Sheet. Manage testing devices i.e. Mobile, tablet.
    \\ \textit{Technology used : Python2.7, Django1.4, Django-Rest-Framework, MySQL, LDAP.}
\end{itemize}


\begin{comment}
\section*{Educational Qualification}
\begin{tabular}{l l c c}
\textbf{Degree} & \textbf{University / Institute} & \textbf{\% Marks} & \textbf{Year}\\[0.2cm]
%& & & \\
B.Tech. & The LNM Institute of Information Technology, Jaipur  & 55.60 & 2012\\[0.2cm]
 %      &  &    &   \\
%& & & \\
Senior Secondary Examination & Maa Bharati Vidhya Bhavan, Kota & 84.92 & 2007\\[0.2cm]
% & & & \\
%& & & \\
Secondary School Examination & Vivek Vardhani Secondary School, Anta  & 86.67 & 2005\\
 & & & \\
\end{tabular}
\end{comment}

\section*{Declaration}
I hereby declare that the above mentioned information is correct up to
my knowledge and I bear the responsibility for the credibility of the particulars.\\
\begin{flushright}
 Anoop Kumar Malav
\end{flushright}
\begin{center}

Last Updated : \today

\end{center}

\end{document}
